---
title: "CodeBook"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset")
```

####Packages

```{r, warning=FALSE, message=FALSE}

library(tidyverse)

```


###1 Description of the dataset

The "Human Activity Recognition" dataset is built from the recordings of 30 subjects performing activities of daily living while carrying a waist-mounted smartphone with embedded inertial sensors. The dataset is available at the following URL: https://archive.ics.uci.edu/ml/machine-learning-databases/00240/UCI%20HAR%20Dataset.zip

The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers were selected for generating the training data and 30% the test data.

The sensor signals (accelerometer and gyroscope) were pre-processed by applying noise filters and then sampled in fixed-width sliding windows of 2.56 sec and 50% overlap (128 readings/window). The sensor acceleration signal, which has gravitational and body motion components, was separated using a Butterworth low-pass filter into body acceleration and gravity. The gravitational force is assumed to have only low-frequency components, therefore a filter with 0.3 Hz cutoff frequency was used. From each window, a vector of features was obtained by calculating variables from the time and frequency domain.

Data:

- "features": List of all features.
- "subject_train"/"subject_test": An ID of the subject who carried out the experiment. 
- "y_train/"y_test": The activity labels. 
- "X_train"/"X_test": The training and the testing data. 


###2 Load the data in RStudio

The first task is to load the training and test datasets into RStudio, each in their own data frame. 

```{r}

X_train = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/train/X_train.txt", quote="\"", comment.char="")

y_train = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/train/y_train.txt", quote="\"", comment.char="")

subject_train = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/train/subject_train.txt", quote="\"", comment.char="")

X_test = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/test/x_test.txt", quote="\"", comment.char="")

y_test = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/test/y_test.txt", quote="\"", comment.char="")

subject_test = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/test/subject_test.txt", quote="\"", comment.char="")

features = read.table("C:/Users/X1/Desktop/Springboard Data/UCI HAR Dataset/features.txt", quote="\"", comment.char="")

```


###3 Merge data sets

Initially, the column names (variables) will be assigned to `x_train/x_test`. The column names for both data sets are the values of the variable `features` because they represent the different measurements.  
```{r}
glimpse(features)
```

```{r}

colnames(X_train) = features$V2
colnames(X_test) = features$V2

```


As you can see, the columns (variables) of `y_train/y_test` and the `subject_train/subject_test` have the same names.
```{r}
colnames(y_train)
colnames(y_test)
colnames(subject_train)
colnames(subject_test)
```


Since `subject_train/subject_test` are the ID´s of `y_train/y_test` they have to be merged. This is only possible if the names of the columns are distinct. 
Therefore they will be renamed. 
```{r}

y_train = rename(y_train, activity = V1)
y_test = rename(y_test, activity = V1)

subject_train = rename(subject_train, subject = V1)
subject_test = rename(subject_test, subject = V1)

```


Then, the activity labels and the subjects will be added to the training and testing data. 
```{r}

train = cbind(subject_train, y_train, X_train)
test = cbind(subject_test, y_test, X_test)

```


Now, the training and the test sets will be be merged to create one data set. 
```{r}

total = rbind(train, test)

```


###4 Mean and standard deviation

The next task is to create two new columns, containing the mean and standard deviation for each measurement respectively. To handle this all columns will be filtered out "which contains a mean ("mean") or a standard ("std") derivation. 
```{r}

column_names = make.names(names=names(total), 
                           unique=TRUE, 
                           allow_ = TRUE)

names(total) = column_names

total_mean_std = total %>% select(activity, 
                                  subject, 
                                  contains("mean"), 
                                  contains("std"))


total_mean_std[1:6] %>% head()

```


###5 Adding new variables

Now, two new variables will be created called `ActivityLabel` and `ActivityName` which label all observations with the corresponding activity labels and names respectively. 

```{r}

total_new_columns = total_mean_std %>% 
  rename(ActivityLabel = activity)


total_new_columns = total_new_columns %>% 
  mutate(ActivityName = ifelse(ActivityLabel == 1, "WALKING", 
                        ifelse(ActivityLabel == 2, "WALKING_UPSTAIRS", 
                        ifelse(ActivityLabel == 3, "WALKING_DOWNSTAIRS", 
                        ifelse(ActivityLabel == 4, "SITTING",
                        ifelse(ActivityLabel == 5, "STANDING",
                        ifelse(ActivityLabel == 6, "LAYING", NA)))))))

total_new_columns = total_new_columns %>% 
  select(subject, 
         ActivityName, 
         ActivityLabel, 
         everything())

total_new_columns[1:2] %>% 
  head()

```

###6 Creating tidy data set

Finally, an independent tidy data set with the average of each variable for each activity and each subject has to be created. For this task, only the variables `subject`, `ActivityLabel` and `ActivityName` will be selected. Moreover, all variables will be selected which contains the character "mean". 
```{r}

tidy_data_set = total_new_columns %>% 
  select(subject, ActivityLabel, ActivityName, contains("mean"))

save(tidy_data_set,file="tidy_data_set.Rda")

```

