---
title: "Exploratory Data Analisis"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("C:/Users/X1/Desktop/Springboard Data/Yelp/yelp.Rda")
```

####Packages
```{r, message=FALSE, warning=FALSE}

library(tidyverse)
```

```{r}

glimpse(yelp)
```


# Questions of the EDA

Demand: 
 
  - Which categories have the greatest demand (review count)?
 
  - Where (city,state) is the greatest demand (review counts)? 

Popularity:
 
  - Which categories are most popular (stars)?
 
  - Which categories with the greatest demand are most popular (stars)?
 
  - Which categories in which states are most popular (stars)?
 
  - Which categories in which cities are most popular (stars)?

Competition:
 
  - Where is the biggest competition (restaurant appearance)?

Success:
 
  - Exploring the relationship between stars, review count and open/closed. 


#1 Demand 

##1.1 Distribution of Review Counts

Distribution of review counts and mean review counts. 
```{r}
mean_review_count = mean(yelp$review_count)

yelp %>%
  ggplot(aes(x = review_count)) +
  geom_histogram(binwidth = 100, boundary = 0) +
  xlim(0, 1500) +
  geom_vline(aes(xintercept = mean_review_count),
               linetype="dashed", colour="red", size=1) +
  theme_minimal() 
```


##1.2 Demand per category

Number of reviews per category. 
```{r}

yelp %>%
  unnest(categories) %>%
  group_by(categories) %>%
  summarise(sum_review_count =  sum(review_count)) %>%
  ggplot(aes(x = reorder(categories, sum_review_count), y = sum_review_count)) +
  geom_bar(stat = "identity") +
  labs(x = "categories", y = "review count") +
  coord_flip() +
  theme_minimal()

```

##1.3 Demand per state

Number of reviews per category per state (Top 5). 
```{r}

yelp %>%
  unnest(categories) %>%
  group_by(state, categories) %>%
  summarise(review_count = sum(review_count)) %>%
  top_n(5, review_count) %>%
  ggplot(aes(x = reorder(state, review_count), 
             y = review_count, 
             fill = categories)) +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "state", y = "review count") +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_minimal()


```

##1.4 Demand per city

Number of review counts per category (Top 5) in the cities with the most review counts (Top 10). 
```{r}
cities = yelp %>%
  group_by(city) %>%
  summarise(n = sum(review_count)) %>%
  arrange(-n) %>%
  head(10)
```

```{r}

yelp %>%
  filter(city %in% cities$city) %>%
  unnest(categories) %>%
  group_by(city, categories) %>%
  summarise(review_count = sum(review_count)) %>%
  top_n(5, review_count) %>%
  ggplot(aes(x = reorder(city, review_count), 
             y = review_count, fill = categories)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "city", y = "review count") +
  coord_flip() +
  theme_minimal()
```

#2 Popularity

##2.1 Distribution of stars

Distribution of stars and the mean of stars. 
```{r}

mean_stars = mean(yelp$stars)

yelp %>%
  count(stars) %>%
  ggplot(aes(x = stars, y = n)) +
  geom_bar(stat = "identity") +
  geom_vline(aes(xintercept = mean_stars),
               linetype="dashed", colour="red", size=1) +
  theme_minimal()
  
```


##2.2 Stars per category

Distribution of stars per category. 
```{r}

rc = yelp %>%
  unnest(categories) %>%
  group_by(categories) %>%
  summarise(review_count = sum(review_count))


rc2 = yelp %>%
    unnest(categories) %>%
    group_by(categories, stars) %>%
    summarise(review_count = sum(review_count))

merge(rc, rc2, by = "categories") %>%
  ggplot(aes(x = reorder(categories, review_count.y), y = review_count.y, fill = as.factor(stars))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "categories", y = "review count", fill = "stars") +
  coord_flip() +
  theme_minimal()

```

##2.3 Mean of stars per state 

Mean of stars in the states with the most review counts (Top 5) per category (Top 5). 
```{r}

yelp %>%
  filter(state %in% c("NV", "AZ", "ON", "NC", "PA")) %>%
  unnest(categories) %>%
  filter(categories %in% c("Asian Fusion", "Japanese", "Chinese", "Thai", "Sushi Bars")) %>%
  group_by(state, categories) %>%
  summarise(mean_stars = mean(stars)) %>%
  ggplot(aes(y = mean_stars, 
             x = reorder(state, mean_stars), 
             fill = categories)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "state", y = "mean stars", fill = "categories") +
  theme_minimal() +
  coord_flip()

```


##2.4 Mean stars per city

Mean of stars in the cities with the most review counts (top 10) per category (top 5). 
```{r}

yelp %>%
  filter(city %in% c(cities$city)) %>%
  unnest(categories) %>%
  filter(categories %in% c("Japanese", "Chinese", "Asian Fusion", "Sushi Bars",
                           "Thai")) %>%
  group_by(city, categories) %>%
  summarise(mean_stars = mean(stars)) %>%
  ggplot(aes(x = reorder(city, mean_stars), 
             y = mean_stars, 
             fill = categories)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "categories", y = "mean stars", fill = "categories") +
  coord_flip() +
  theme_minimal()

```


#3 Competition

##3.1 Number of restaurants

Number of restaurants per category. 
```{r}

yelp %>%
  unnest(categories) %>%
  count(categories) %>%
  ggplot(aes(reorder(categories, n), n)) +
  geom_bar(stat = "identity") +
  labs(x = "categories", y = "n") +
  theme_minimal() +
  coord_flip()

```

##3.2 Competition per state

Number of restaurants (Top 5) per state. 
```{r}

yelp %>%
  unnest(categories) %>%
  group_by(state) %>%
  count(categories) %>%
  top_n(5, n) %>%
  ggplot(aes(x = reorder(state, n), y = n, fill = categories)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "state") +
  theme_minimal() +
  coord_flip()

```

##3.3 Number of restaurants per city

Number of restaurants per city (Top 10) per category (Top 5). 
```{r}

yelp %>%
  filter(city %in% cities$city) %>%
  unnest(categories) %>%
  group_by(city) %>%
  count(categories) %>%
  top_n(5, n) %>%
  ggplot(aes(x = reorder(city, n), y = n, fill = categories)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "state") +
  theme_minimal() +
  coord_flip()

```

# 4 Success

##4.1 Relationship between open/closed and review count

Logistic regression between is open and review count. 
```{r}

yelp %>%
  ggplot(aes(x = review_count, y = is_open)) +
  stat_smooth(method = "glm", method.args=list(family="binomial")) +
  scale_x_continuous(limits = c(0, 1500)) +
  theme_minimal()

```

##4.2 Relationship between open/closed and stars

Logistic regression between is open and stars. 
```{r}

yelp %>%
  ggplot(aes(x = stars, y = is_open)) +
  stat_smooth(method = "glm", method.args=list(family="binomial")) +
  theme_minimal()

```

##4.3 Relationship between stars and review count  

Smoothened linear regression between stars and review count. 
```{r, warning=FALSE, message=FALSE}

yelp %>%
  ggplot(aes(x = stars , y = review_count)) +
  geom_point() +
  geom_smooth(method = "loess") +
  theme_minimal()

```


#5 Conclusion

Demand:

   - Overall, the greatest demand has the Japanese category. 
   
   - The greatest demand is in Las Vegas (NV) for the Japanese category. 

Popularity:
  
  - Overall, the Japanese category is most popular. 
  
  - In NV the most popular category is Shushi Bars.
  
  - In Las Vegas the most popular category is Asian Fusion. 

Competition:
  
  - Most of the restaurants are Chinese. 
  
  - The most restaurants are in Toronto (ON). 

Success:
  
  - Stars and review count are a predictor that a busines survives, where review count     is more important.
  
  - There is a strong relationship betweeen stars and review count but only until 4 
    stars. 

